\section{States}
One of the components of a compiled models is \textit{states}.
States is a section that is reserved on the SRAM that is used as a buffer for the accumulation of the activation data.

\todo[inline]{Insert more explanation about states}

We can improve the energy consumption when performing a model configuration by avoiding the reading of the states.
This allows us to read less data from the external memory, reducing the energy for configuration.
Furthermore, this also improves the configuration latency.

We perform an analysis on various models to get an idea of how much we can benefit with avoiding the read of states.
The compiler provides us with the amount of bytes used for the states and other components of each model.

\begin{table}[hbtp]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Model}          & \textbf{States ratio} & \textbf{Prune ratio} \\ \midrule
efficientnet            & 23\%                  & 20\%                 \\
hand\_detector          & 51\%                  & 0\%                  \\
mobnetv2                & 31\%                  & 0\%                  \\
hand\_tracker\_star\_v2 & 28\%                  & 20\%                 \\
resnet50                & 28\%                  & 80\%                 \\
resnet101\_p0           & 24\%                  & 0\%                  \\
resnet101\_p1           & 14\%                  & 0\%                  \\
resnet101\_p2           & 15\%                  & 0\%                  \\
resnet101\_p3           & 8\%                   & 0\%                  \\
resnet101\_p4           & 6\%                   & 0\%                  \\
resnet101\_pruned\_p0   & 44\%                  & 80\%                 \\
resnet101\_pruned\_p1   & 27\%                  & 80\%                 \\
resnet101\_pruned\_p2   & 28\%                  & 80\%                 \\
resnet101\_pruned\_p3   & 14\%                  & 80\%                 \\
resnet101\_pruned\_p4   & 11\%                  & 80\%                 \\ \bottomrule
\end{tabular}
\caption{All model shown are 8-bit quantized}
\label{tab:states_ratio}
\end{table}

Looking at \cref{tab:states_ratio}, on average, $23\%$ is used for states.
We observe that the states ratio can reach half of the total bytes to be written to the GrAICore.
Thus, with the models in \cref{tab:states_ratio}, we can reduce the amount of data to be read from the external memory by up to a half.